\documentclass[12pt]{article}
\usepackage[latin1]{inputenc}
\usepackage{enumerate}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{comment}
\usepackage{alltt}
\usepackage{url}
\usepackage{xcolor}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\newcommand{\NB}[0]{\textcolor{red}{\textbf{!lahde!}}}
\newcommand{\TD}[0]{\textcolor{red}{\textbf{!TODO!}}}
\newcommand{\E}[0]{\textbf{Ebola }}
\lhead{\#41983}
\rhead{\rightmark}
\title{BORA - Balanced Operational Rescue Algorithm}
\author{Team 41983}
\date{}                                           % Activate to display a given date or no date

\begin{document}

\setlength{\parindent}{0cm}

\textbf{Dear Academic Fellows},

It gives us great pleasure to stand amongst the frontier against the Ebola virus. While tackling the anatomy of this vicious pestilence has surely been a true challenge, and we wish to congratulate You thereof. But there are still hardships to overcome. For one, we must be able to take care of the production of the medicine, but also to deal with the ever so important distribution. 

In order to eradicate the virus, we have designed ingenious mathematical model BORA, Balanced Operational Rescue Algorithm, to both accurately predict the evolution of epidemic and effectively determine how a medication plan would damage the spread. With this supreme model, we were able to pinpoint efficient strategies to best the pest.

\TD  

%Without a shadow a doubt

Yours Sincerely \\ Team \#41983


\end{document}
